Meritocracy and distributive preferences ISSP

### 2020-06-03 docs/index.Rmd
Renderizado
se mejoran  los titulos.

se da un mejor orden al documento

se arreglan las tablas

se eliminan output poco parcimoniosos

- The tabs follow the logic of the [IPO protocol](https://github.com/juancarloscastillo/ipo) for academic workflows, based on three main components = **I**nput -> **P**roduction -> **O**utput. Here we show only one the main parts of each component: Data -> Analysis -> Paper. The complete reproducible files are in the [Github repo: https://juancarloscastillo.github.io/merit-scale/](https://juancarloscastillo.github.io/merit-scale/)

>>>>

- The tabs follow the logic of the [IPO protocol](https://github.com/juancarloscastillo/ipo) for academic workflows, based on three main components = **I**nput -> **P**roduction -> **O**utput. Here we show only one the main parts of each component: Data -> Analysis -> Paper. The complete reproducible files are in the [Github repo: https://juancarloscastillo.github.io/meritocracy-preferences/](https://juancarloscastillo.github.io/meritocracy-preferences/)

### 2020-06-03 production/prod_analysis.rmd
Renderizado
se mejoran  los titulos.

se da un mejor orden al documento

se arreglan las tablas

se eliminan output poco parcimoniosos

# Descriptives
```{r results='asis'}
  # Summary table
    stargazer(redistrib[-c(1,2)], type="html")

  # Summary table to latex
    sink("output/results/desctab_red.txt")
    stargazer(redistrib[-c(1,2)], type="text"); sink()

  # Simple graph:
    sjPlot::plot_frq(redistrib$income_dif, show.values = TRUE, coord.flip = TRUE)

@@

```{r echo=FALSE}
# Likert graph 
    sjPlot::plot_frq((redistrib[3:7])) # ajustar

    # short var labels
    items <- c("Gov. reduce income dif.", "Gov. decent unemp.",
               "High income taxes", "Buy better health", 
               "Buy better education")

    # cambiar orden para la leyenda  
    labels= c("Strongly agree", "Agree", "Disagree",
              "Strongly disagree", "(neither/nor)" )  ### E

    # ajustes globales sjplot
    sjPlot::set_theme(theme         = "blank",
                      legend.inside = TRUE, 
                      legend.pos    = "bottom right", legend.size = 0.8,
                      geom.outline.size=0, geom.label.size =3)

    sjPlot::plot_likert((redistrib[3:7]), 
                        axis.labels   = items,
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                          "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Agree / disagree ...",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = FALSE, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.40) # expand axis 130% )

    # Save
    #dev.copy(png,"output/results/likert_red.png",width=800); dev.off()

```{r}
# 2.3 Measurement structure

@@

	fit_red1 <- cfa(cfa_red1,data=redistrib, missing = "ML") 
#	summary(fit_red1, fit.measures=TRUE,standardized=TRUE)

		# Path

			semPlot::semPaths(fit_red1,layout = "tree2", rotation = 2, 
	  	intercepts = FALSE,	style = "lisrel", curvePivot = TRUE,
	  	cardinal = TRUE)
		  dev.copy(png,"output/results/path_red1.png",width=750,height=600)
		  dev.off()	  	  	 
## ## ## ## ### ##                                            ### ## ## ## ##ARREGLAR LOS DIAGRAMAS. 
		# Path - with results
		  semPlot::semPaths(fit_red1,"std",layout = "tree2", rotation = 2, 
	  	intercepts = FALSE,	style = "lisrel", curvePivot = TRUE,
	  	cardinal = TRUE, edge.color = "black", residScale = 10)
		  dev.copy(png,"output/results/path_red1_res.png",
		  	width=750,height=600); dev.off()

	# Categorical	  
		fit_red1c <- cfa(cfa_red1,data=redistrib, 
			ordered = c("income_dif","unemployed","taxes", "health", 
			"educ")) 
	#	summary(fit_red1c, fit.measures=TRUE,standardized=TRUE)
#

sum_fit<- bind_rows(fitmeasures(fit_red1)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])

sum_fit$mod <- c("Model 1")
sum_fit$est <- c("MLR")
#sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: fixed order by percepction/preferenc"))
sumtable01

		# 2.4 Factor scores --------------------- --------

	# Multiple imputation (para recuperar missings en scores)

@@

```{r}
# 4. MODELS A:  MERIT & REDISTRIB ========= =

# 4.1 Merge objects --------------------- ---- 
	load("input/data/proc/redistrib.rda")
	load("input/data/proc/getahead.rda")                       
	load("input/data/proc/detearn.rda")

@@

# 4.2 Measurement & structural model ---- --------

@@

	  	# Path
	 		  semPlot::semPaths(fit_mer_red1,layout = "circle", rotation = 3, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
	 		  dev.copy(png,"output/results/path_mer_red1.png",width=800,
		    	height=650);  dev.off()

@@

sum_fit<- bind_rows(fitmeasures(fit_mer_redc)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])

sum_fit$mod <- c("Model 1")
sum_fit$est <- c("MLR")
#sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: fixed order by percepction/preferenc"))
sumtable01

@@

	  cfa_mer_red2 <- '
	  # latent variables
		  merit =~ hwork + ambition 
		  parent=~ wealthy + pareduc
		  backg=~ race + gender
			network=~ people + polcone
		  bmerit =~ welljob + hardjob 
		  need=~ family + child
			redist =~ income_dif + unemployed + taxes 
	  	accum  =~ health + educ
			unmerit =~ parent + backg + network
	  '     
	  fit_mer_red2 <- cfa(cfa_mer_red2,data=merit_redist, 
	  	missing = "ML") 
#	  summary(fit_mer_red2, fit.measures=TRUE,standardized=TRUE)

	sum_fit<- bind_rows(fitmeasures(fit_mer_red2)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])

sum_fit$mod <- c("Model 1")
sum_fit$est <- c("MLR")
#sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: fixed order by percepction/preferenc"))
sumtable01  
	    # Factor scores
	  fscores <- as.data.frame(lavPredict(fit_mer_red2))

@@

	  #  Path
	 		  semPlot::semPaths(fit_mer_red2,layout = "tree", rotation = 2, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
	 		  dev.copy(png,"output/results/path_mer_red2.png",width=800,
		    	height=650);  dev.off()

@@

```{r}
# 5.2 Descriptives 
	load("input/data/proc/pref.rda")

@@

```{r}
# 5.3 Models

@@

sum_fit<- bind_rows(fitmeasures(fit_2c)[c("chisq.scaled","df","cfi","cfi.scaled","cfi.robust","rmsea","rmsea.scaled","rmsea.robust")])

sum_fit$mod <- c("Model 1")
sum_fit$est <- c("MLR")
#sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi^2$","df","CFI","CFI.sca","CFI.rob","RMSEA","RMSEA.sca","RMSEA.rob")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: fixed order by percepction/preferenc"));
sumtable01

@@

# 6. MODELS C: MERITOCRACY

# 6.2 Descriptives

@@

      ##### la mayoria de los str.scatter precentan problemas en los limites "subindice fuera de limites.

@@

```{r}
  # Sin outliers

@@

```{r results='asis' , message= F}
# 6.3 Models

@@

	# check simple regresion
	  ols_merit=lm(merit ~ univ + Quintile + sstatus + gini_net, data = meritocracy)
	  summary(ols_merit) # ok, similar SEM, scores OK

>>>>

# Descriptives
```{r results='asis'}
  # Summary table to latex
    sink("output/results/desctab_red.html")
    stargazer(redistrib[-c(1,2)], type="html"); sink()
```

## plot likert 
```{r echo=FALSE}
     # short var labels
    items <- c("Gov. reduce income dif.", "Gov. decent unemp.",
               "High income taxes", "Buy better health", 
               "Buy better education")

    # cambiar orden para la leyenda  
    labels= c("Strongly agree", "Agree", "Disagree",
              "Strongly disagree", "(neither/nor)" )  ### E
    png<-sjPlot::plot_likert((redistrib[3:7]), 
                        axis.labels   = items,
                        legend.labels = labels,
                        cat.neutral   = 5, # identifica a indiferentes
                        geom.colors   = c("#9ecae1", "#6baed6","#4292c6", 
                                          "#2171b5"), # colorbrewer2.org 
                        sort.frq      = "neg.asc", # sort descending)
                        title         = "Agree / disagree ...",
                        intercept.line.color = "white", # vertical middle
                        expand.grid   = F, # no inner margins in plot
                        show.n        = FALSE, # hide N's in axis labels
                        grid.range    = 1.8,
                        geom.size = 0.6) # expand axis 130% )

    # Save
    ggsave(png,filename = "output/images/plotlikert.png",device = "png", width=25, units = "cm")

@@

![](../output/images/plotlikert.png)

@@

	fit_red1 <- cfa(cfa_red1,data=redistrib, missing = "ML") 
#summary(fit_red1, fit.measures=TRUE,standardized=TRUE)

#fitmeasures(fit_red1)

### Measurement structure

```{r}
		# Path 
			semPlot::semPaths(fit_red1,layout = "tree2", rotation = 2, 
	  	intercepts = FALSE,	style = "lisrel", curvePivot = TRUE,
	  	cardinal = TRUE)
	#	  dev.copy(png,"output/results/path_red1.png",width=750,height=600)
		#  dev.off()	  	  	 
## ## ## ## ### ##                                            ### ## ## ## ##ARREGLAR LOS DIAGRAMAS.

## Fit cfa model
```{r}

sum_fit<- bind_rows(fitmeasures(fit_red1)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])
sum_fit

colnames <- c("$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle");sumtable01
```

```{r}
		# Path - with results
		  semPlot::semPaths(fit_red1,"std",layout = "tree2", rotation = 2, 
	  	intercepts = FALSE,	style = "lisrel", curvePivot = TRUE,
	  	cardinal = TRUE, edge.color = "black", residScale = 10)
#		  dev.copy(png,"output/results/path_red1_res.png",
#		  	width=750,height=600); dev.off()

	# Categorical	  
		fit_red1c <- cfa(cfa_red1,data=redistrib, 
			ordered = c("income_dif","unemployed","taxes", "health", 
			"educ")) 
	#	summary(fit_red1c, fit.measures=TRUE,standardized=TRUE)
# 	                                      
```

### 2.4 Factor scores 
```{r}
	# Multiple imputation (para recuperar missings en scores)

@@

# MODELS A:  MERIT & REDISTRIB
```{r}
# 4.1 Merge objects --------------------- ---- 
	load("input/data/proc/redistrib.rda")
	load("input/data/proc/getahead.rda")                       
	load("input/data/proc/detearn.rda")

@@

```{r}
# 4.2 Measurement & structural model ---- --------

@@

	  	# Path
	 		  semPlot::semPaths(fit_mer_red1,layout = "circle", rotation = 3, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
	# 		  dev.copy(png,"output/results/path_mer_red1.png",width=800,
	#	    	height=650);  dev.off()

@@

@@

	  cfa_mer_red2 <- '
	  # latent variables
		  merit =~ hwork + ambition 
		  parent=~ wealthy + pareduc
		  backg=~ race + gender
			network=~ people + polcone
		  bmerit =~ welljob + hardjob 
		  need=~ family + child
			redist =~ income_dif + unemployed + taxes 
	  	accum  =~ health + educ
			unmerit =~ parent + backg + network
	  '     
	  fit_mer_red2 <- cfa(cfa_mer_red2,data=merit_redist, 
	  	missing = "ML") 
#	  summary(fit_mer_red2, fit.measures=TRUE,standardized=TRUE)
```

```{r}
sum_fit<- bind_rows(fitmeasures(fit_mer_redc)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")],
                    fitmeasures(fit_mer_red2)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])
sum_fit$mod <- c("Model 1","Model 2")
sum_fit$est <- c("MLR","DWLS")
#sum_fit <- select(sum_fit,mod,est,everything())
colnames <- c("Model","Estimator","$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")
 sum_fit

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle")  %>%
      footnote(number = c("Model 1: Continue item",
                          "Model 2: Ordered item)"));sumtable01

	    # Factor scores
	  fscores <- as.data.frame(lavPredict(fit_mer_red2))

@@

	  #  Path
	 		  semPlot::semPaths(fit_mer_red2,layout = "tree", rotation = 2, 
			  	intercepts = FALSE, style = "lisrel", curvePivot = TRUE,
			  	sizeMan = 4, sizeLat = 6)
	 		#  dev.copy(png,"output/results/path_mer_red2.png",width=800,
		   # 	height=650);  dev.off()

@@

#  Descriptives

	load("input/data/proc/pref.rda")

@@

# Models
```{r}

@@

sum_fit<- bind_rows(fitmeasures(fit_red1)[c("chisq","df","cfi","rmsea","rmsea.ci.lower","rmsea.ci.upper")])
sum_fit

colnames <- c("$\\chi2$","df","CFI","RMSEA","RMSEA CI lower", "RMSEA CI upper")

sumtable01<- kable(sum_fit,digits = 3,format = "html",row.names = F,booktabs=T, caption = "Summary fit indices wave 01",col.names = colnames,escape = FALSE) %>%
  kable_styling(full_width = F)  %>%
      collapse_rows(columns = 1,valign = "middle");sumtable01

@@

#  MODELS C: MERITOCRACY
##  Descriptives

```{r}
    load("input/data/proc/meritocracy.rda")

@@

@@

#### Graficos sin outliers
```{r}

@@

##  Models

```{r results='asis'}

@@

	# check simple regresion
	  ols_merit=lm(merit ~ univ + Quintile + sstatus + gini_net, data = meritocracy)
	  stargazer(ols_merit, type ="html") # ok, similar SEM, scores OK
```

```{r results='asis' , message= F}
